Supervision

### 2024-06-21 done.qmd
update

>>>>

2024-06-21: Research Matters magazine (with Shaun Leamon): [Experiments in research funding to reduce research](https://the-sra.org.uk/common/Uploaded%20files/Research%20Matters%20Magazine/sra-research-matters-june-2024-edition.pdf) bureaucracy

2024-06-18: Early results from our project with Volkswagen Foundation: [Researchers optimistic about Distributed Peer Review](https://researchonresearch.org/dpr-volkswagen-foundation-first-results/)

2024-06-17: Hosted [AI replication game](https://sites.google.com/sheffield.ac.uk/orwg/research-practice) at University of Sheffield with the [Institute for Replication](https://i4replication.org/)

2024-05-23: Organised networking event for [University of Sheffield editors](https://sites.google.com/sheffield.ac.uk/orwg/research-practice)

2024-06-21: [2024 Showcase for Data Analysis and Visualisation MSc Students](https://tomstafford.github.io/psy6422/class-of-2024.html)

### 2024-06-21 supervision.qmd
update

@@

# Examining

@@

-   Andrea Caso, Birkbeck, University of London, 1 July 2019**

>>>>

- [Adam Partridge](https://orcid.org/0000-0002-0133-4155) (2022 -), as Open Research Training Lead for the University of Sheffield and part of the [UKRN Open Research Programme](https://www.ukrn.org/open-research-programme/)

@@

# PhD Examining

@@

-   **Andrea Caso, Birkbeck, University of London, 1 July 2019**
